Quantitative, Multispecies Monitoring at a Continental Scale

### 2025-02-11 SI_Appendix.tex
Updates from Overleaf

\title{Quantitative, Multispecies Monitoring at a Continental Scale}
\author{Gledis Guri, Owen Liu, Ryan P. Kelly, Megan Shaffer, Kim Parsons, Ana Ram\'on-Laca,\\
Krista M. Nichols, Pedro F. P. Brandão-Dias and Andrew Olaf Shelton}
\correspondingauthor{Gledis Guri.\\E-mail: gguri@uw.edu}

@@

\section*{Extended Methods}
\subsection*{qPCR}
Environmental samples were analyzed in triplicate using the multiplexed assay targeting Pacific hake, Eulachon and Pacific lamprey as described in \cite{ramon-laca2021} on a QuanStudio 6 (Applied Biosystems). Only Pacific hake qPCR data was used in this study due to the remaining qPCR targets having little positive amplification. The samples underwent real-time thermocycler protocol including an initial denaturation step at 95°C 10 min followed by 40 cycles of 15 s at 95°C and 1 min at 58°C. All thermocycler reactions were run in 20 $\mu$L volume consisting of 10 $\mu$L of TaqMan Environmental Master Mix 2.0, 1 $\mu$L of each primer (forward: AAATGTTTAAACTAGAGCCGAATAGC and reverse: TCGTGGAGTCAAAGTGGGGTAGA, 10 nM concentration each), 0.5 $\mu$L of probe (AAATGTTTAAACTAGAGCCGAATAGC; 10nM concentration), 3 $\mu$L of dH20 and 2 $\mu$L of DNA template. To monitor quality control, all runs included an internal positive control (IPC) to detect PCR inhibition and a negative template control (NTC) containing water instead of DNA template. Any IPC delay exceeding 0.5 cycles in the NTC was considered inhibition and inhibited samples were diluted and re-analyzed.

Alongside environmental samples standard samples were analyzed constructed from a 120 bp synthetic DNA fragment (gBlock; IDT) representing the 12S region of Pacific hake (\textit{Merluccius productus}), which encompasses the 101 bp 12S qPCR target (sequence information available in Ramón-Laca et al. 2021). The synthetic DNA fragment was diluted to create a series of standards with final concentrations ranging from $10^{0}$ to $10^{5}$ copies/$\mu$L.

>>>>

\title{Quantitative, Multispecies Monitoring at a Continental Scale}
\author{Gledis Guri, Owen Liu, Ryan P. Kelly, Megan Shaffer, Kim Parsons, Ana Ram\'on-Laca,\\
Krista M. Nichols, Pedro F. P. Brandão-Dias, Abigail Wells and Andrew Olaf Shelton}
\correspondingauthor{Gledis Guri.\\E-mail: gguri@uw.edu}

@@

\section*{Extended Methods}
\subsection*{qPCR}
Environmental samples were analyzed in triplicate using the multiplexed assay targeting Pacific hake, Eulachon and Pacific lamprey as described in \cite{ramon-laca2021} on a QuanStudio 6 (Applied Biosystems). Only Pacific hake qPCR data was used in this study due to the remaining qPCR targets having little positive amplification.

The samples underwent real-time thermocycler protocol including an initial denaturation step at 95°C 10 min followed by 45 cycles of 15 s at 95°C and 1 min at 60°C. All samples were run in triplicate in 10 $\mu$L volume consisting of 1 x TaqPath ProAmp Multiplex Master Mix, 0.9 $\mu$M of each primer (forward: AAATGTTTAAACTAGAGCCGAATAGC and reverse: TCGTGGAGTCAAAGTGGGGTAGA), 0.2 $\mu$M of probe (6FAM-CACTCGAGGCCACGAAGTACAATT-(MGB)NFQ), and 2 $\mu$L of DNA template or water for the non-template control. All reactions included 100 copies of internal positive control (IPC) to detect PCR inhibition. Any IPC delay exceeding 0.5 cycles in the non-template control was considered inhibition and inhibited samples were diluted and re-analyzed.

Alongside environmental samples standard samples were analyzed constructed from a 130 bp synthetic DNA fragment (gBlock; IDT) representing the 12S region of Pacific hake (\textit{Merluccius productus}), which encompasses the 101 bp 12S qPCR target (sequence information available in \cite{ramon-laca2021}). The synthetic DNA fragment was diluted to create a series of standards with final concentrations ranging from $10^{0}$ to $10^{5}$ copies/$\mu$L.
